Reliable feature point matching

### 2013-08-10 text/main/ch5_experiments.tex
Updated thesis with spectral-mmc info and better figures

\begin{figure}[htb]
	\makebox[0.5\textwidth][c]{%
		\begin{subfigure}[t]{.13\textwidth}
			\centering
			\includegraphics[width=\textwidth]{images/graf}
		\end{subfigure}%
		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
   	%(or a blank line to force the subfigure onto a new line)
		\begin{subfigure}[t]{.27\textwidth}
   		\centering
   		\includegraphics[width=0.6\columnwidth]{images/result_graf}
   		%\caption{Performance on Scharf}
		\end{subfigure}%
	}%
	\caption{Accuracy for image pair 1\&3 from the \emph{Graf} set. The plot 
		shows the result of 100 patch pairs generated from the source 
		images shown to the left. The number of matches is the total 
		number of matches for all 100 patch pairs.}
	\label{fig:result_graf}
\end{figure}

@@

\begin{figure}[htb]
	\centering
	\includegraphics[width=0.45\textwidth]{images/result_viewpoint}
	\caption{Results for viewpoint changes using the \emph{Graf} set from 
		\cite{mikolajczyk2005performance}.  S: img1\&2; M: img1\&3; L: img1\&4; XL: img1\&5.}
	\label{fig:result_viewpoint}
\end{figure}

@@

\begin{figure}[htb]
	\makebox[\textwidth][c]{%
		\begin{subfigure}[t]{.2\textwidth}
			\centering
			\includegraphics[width=\textwidth]{images/pitts}
		\end{subfigure}%
		~%add desired spacing between images, e. g. ~, \quad, \qquad
		%(or a blank line to force the subfigure onto a new line)
		\begin{subfigure}[t]{.8\textwidth}
   		\centering
   		\includegraphics[width=0.6\columnwidth]{images/result_pitts}
		\end{subfigure}%
	}%
	\caption{Results for the image pair in Figure~\ref{fig:pitts_source}.}
	\label{fig:result_pitts}
\end{figure}

>>>>

\begin{figure}[htb]
	\begin{subfigure}[c]{0.2\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/graf}
	\end{subfigure}%
	~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
	%(or a blank line to force the subfigure onto a new line)
	\begin{subfigure}[c]{0.8\textwidth}
	\centering
	\includegraphics[width=\columnwidth]{images/result_graf}
	%\caption{Performance on Scharf}
	\end{subfigure}%
	\caption{Accuracy for image pair 1\&3 from the \emph{Graf} set. The 
	plot shows the result of 100 patch pairs generated from the source 
images shown to the left. The number of matches is the total number of 
matches for all 100 patch pairs.}
	\label{fig:result_graf}
\end{figure}

@@

\begin{figure}[htb]
	\centering
	\includegraphics[width=1\textwidth]{images/result_viewpoint}
	\caption{Results for viewpoint changes using the \emph{Graf} set 
	from \cite{mikolajczyk2005performance}.  S: img1\&2; M: img1\&3; L: 
	img1\&4; XL: img1\&5.}
	\label{fig:result_viewpoint}
\end{figure}

In order to investigate whether a geometric algorithm can be improved by
pruning the initial matching set, we tested a hybrid algorithm 
\emph{Spectral-MMC} where matches are pruned by \emph{MMC} before being 
applied to \emph{Spectral}. The results are shown in 
Figure~\ref{fig:result_spectral-mmc} and show that \emph{Spectral-MMC} 
not only outperforms \emph{Spectral} but also improves on \emph{MMC} at 
similar recall rates, illustrating how a geometric algorithm can be 
complemented by a reliable non-geometric pruning of matches.
\begin{figure}[htb]
	\centering
	\includegraphics[width=1\textwidth]{images/result_spectral-mmc}
	\caption{Results for filtering matches with \emph{MMC} before 
	applying the \emph{Spectral} algorithm.}
	\label{fig:result_spectral-mmc}
\end{figure}

@@

\begin{figure}[htb]
	\begin{subfigure}[c]{.2\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/pitts}
	\end{subfigure}%
	~%add desired spacing between images, e. g. ~, \quad, \qquad
	%(or a blank line to force the subfigure onto a new line)
	\begin{subfigure}[c]{.8\textwidth}
	\centering
	\includegraphics[width=1\columnwidth]{images/result_pitts}
	\end{subfigure}%
	\caption{Results for the image pair in 
	Figure~\ref{fig:pitts_source}.}
	\label{fig:result_pitts}
\end{figure}
